|

### 2023-06-29 full-paper/paper.Rmd
latex: update Code environment setup

hooks <- knitr::knit_hooks$get("source")
knitr::knit_hooks$set(source = function(x, options) {
  x <- hooks(x, options)
  x <- ifelse(!is.null(options$code.ref), paste0("\\label{", options$code.ref, "}", x), x)
  ifelse(!is.null(options$code.cap), paste0("\\captionof{code}{", options$code.cap, "}", x), x)
})
```

>>>>

hooks <- knitr::knit_hooks$get("source")
knitr::knit_hooks$set(source = function(x, options) {
  x <- hooks(x, options)
  if (!is.null(options$code.ref)) {
    x <- paste0("\\label{", options$code.ref, "}", x)
  }
  if (!is.null(options$code.cap)) {
    x <- paste0(c(
      "```{=latex}\n",
      "\\begin{Code}\n",
      "\\caption{", options$code.cap, "}\n",
      "```\n",
      x,
      "```{=latex}\n",
      "\\end{Code}\n",
      "```"
    ))
  }
  x
})
```
